---
title: "Basic Estimations"
author: "Kyohei Sato"
date: "2024-09-14"
output: html_document
---

```{r setup, include=FALSE}
pacman::p_load(tidyverse, here, DT, outliers, ggridges, estimatr, fixest)

dat_basic <- 
  read_csv(here::here("/masters_thesis/data/panel/dat_basic.csv"))

## Data Processing
dat_basic <- 
  dat_basic |> 
  filter(wage_per_hour > 700, wage_per_hour < 10000) |> 
  mutate(treat = if_else(year >= 2020, 1, 0))

```


## Estimated Model

- Consider the situation that the timing of policy intervention across individuals are equal.
- $y_{i,t}$ is the outcome variable of worker $i$, in year $t$. $T^*$ is the year of treatment and $\beta_{T^* -1}$ is normalised to zero. 

$$
\begin{equation*}
y_{i,t} = \alpha_i + \delta_t + \sum_{r \neq T^* -1} \mathbb{1}(t = r) Treated_i \times \beta_r + \epsilon_{i, t}
\end{equation*}
$$

## Wage Change wo control {.tabset}
### Regular vs Dispatched
```{r, echo=FALSE, message=FALSE}

dat_reg_disp <- dat_basic |> filter(regular == 1 | dispatched == 1)

reg1 <- 
  feols(logwage~ i(year,dispatched, ref=2019) | ID+year, data = dat_reg_disp)

iplot(reg1)

```

### Part-time vs Dispatched
```{r, echo=FALSE, message=FALSE}

dat_pt_disp <- dat_basic |> filter(part_time == 1 | dispatched == 1)

reg2 <- 
  feols(logwage~ i(year,dispatched, ref=2019) | ID+year, data = dat_pt_disp)

iplot(reg2)

```

### Fixed-term vs Dispatched
```{r, echo=FALSE, message=FALSE}

dat_ft_disp <- dat_basic |> filter(fixed_term == 1 | dispatched == 1)

reg3 <- 
  feols(logwage~ i(year,dispatched, ref=2019) | ID+year, data = dat_ft_disp)

iplot(reg3)

```

### Shokutaku vs Dispatched
```{r, echo=FALSE, message=FALSE}

dat_sho_disp <- dat_basic |> filter(shokutaku == 1 | dispatched == 1)

reg4 <- 
  feols(logwage~ i(year,dispatched, ref=2019) | ID+year, data = dat_sho_disp)

iplot(reg4)

```

## Wage Change controlling born year and college education {.tabset}
### Regular vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg5 <- 
  feols(logwage~ i(year,dispatched, ref=2019) + 
          edu_cg + born_year| 
          ID+year
        , data = dat_reg_disp)

iplot(reg5)

```

### Part-time vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg6 <- 
  feols(logwage~ i(year,dispatched, ref=2019) +
          ID+year|
          ID+year,
        data = dat_pt_disp)

iplot(reg6)

```

### Fixed-term vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg7 <- 
  feols(logwage~ i(year,dispatched, ref=2019) +
          ID+year|
          ID+year,
        data = dat_ft_disp)

iplot(reg7)

```

### Shokutaku vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg8 <- 
  feols(logwage~ i(year,dispatched, ref=2019) +
          ID+year|
          ID+year,
        data = dat_sho_disp)

iplot(reg8)

```





## OJT Change wo control {.tabset}
### Regular vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg9 <- 
  feols(d_OJT~ i(year,dispatched, ref=2019) | ID+year, data = dat_reg_disp)

iplot(reg9)

```

### Part-time vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg10 <- 
  feols(d_OJT~ i(year,dispatched, ref=2019) | ID+year, data = dat_pt_disp)

iplot(reg10)

```

### Fixed-term vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg11 <- 
  feols(d_OJT~ i(year,dispatched, ref=2019) | ID+year, data = dat_ft_disp)

iplot(reg11)

```

### Shokutaku vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg12 <- 
  feols(d_OJT~ i(year,dispatched, ref=2019) | ID+year, data = dat_sho_disp)

iplot(reg12)

```


## Wage Change controlling born year and college education {.tabset}
### Regular vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg13 <- 
  feols(d_OJT~ i(year,dispatched, ref=2019) + 
          edu_cg + born_year| 
          ID+year
        , data = dat_reg_disp)

iplot(reg13)

```

### Part-time vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg14 <- 
  feols(d_OJT~ i(year,dispatched, ref=2019) +
          ID+year|
          ID+year,
        data = dat_pt_disp)

iplot(reg14)

```

### Fixed-term vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg15 <- 
  feols(d_OJT~ i(year,dispatched, ref=2019) +
          ID+year|
          ID+year,
        data = dat_ft_disp)

iplot(reg15)

```

### Shokutaku vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg16 <- 
  feols(d_OJT~ i(year,dispatched, ref=2019) +
          ID+year|
          ID+year,
        data = dat_sho_disp)

iplot(reg16)

```



## OFF-JT Change wo control {.tabset}
### Regular vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg17 <- 
  feols(d_OFF_JT~ i(year,dispatched, ref=2019) | ID+year, data = dat_reg_disp)

iplot(reg17)

```

### Part-time vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg18 <- 
  feols(d_OFF_JT~ i(year,dispatched, ref=2019) | ID+year, data = dat_pt_disp)

iplot(reg18)

```

### Fixed-term vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg19 <- 
  feols(d_OFF_JT~ i(year,dispatched, ref=2019) | ID+year, data = dat_ft_disp)

iplot(reg19)

```

### Shokutaku vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg20 <- 
  feols(d_OFF_JT~ i(year,dispatched, ref=2019) | ID+year, data = dat_sho_disp)

iplot(reg20)

```


## Wage Change controlling born year and college education {.tabset}
### Regular vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg21 <- 
  feols(d_OFF_JT~ i(year,dispatched, ref=2019) + 
          edu_cg + born_year| 
          ID+year
        , data = dat_reg_disp)

iplot(reg13)

```

### Part-time vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg22 <- 
  feols(d_OFF_JT~ i(year,dispatched, ref=2019) +
          ID+year|
          ID+year,
        data = dat_pt_disp)

iplot(reg22)

```

### Fixed-term vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg23 <- 
  feols(d_OFF_JT~ i(year,dispatched, ref=2019) +
          ID+year|
          ID+year,
        data = dat_ft_disp)

iplot(reg23)

```

### Shokutaku vs Dispatched
```{r, echo=FALSE, message=FALSE}

reg24 <- 
  feols(d_OFF_JT~ i(year,dispatched, ref=2019) +
          ID+year|
          ID+year,
        data = dat_sho_disp)

iplot(reg24)

```