---
title: "Callaway and Sant'Anna sample -5 to -1"
author: "Kyohei Sato"
date: "2024-11-21"
output: html_document
---

## 介入を受ける5年前から1年前すべてに雇用期間のある()サンプルをもちいた

```{r setup, include=FALSE}
# Install packages

if (!require(pacman)) install.packages("pacman")
pacman::p_load(
  cem, cobalt, fixest, gtExtras, here,
  labelled, RColorBrewer, rlist, scales, tidyverse, estimatr, modelsummary,
  fastDummies, did, DT, lfe
)
pacman::p_load_gh("rstudio/gt")

# Read and clean data

df_basic <- 
  read_csv(here::here("/masters_thesis/data/panel/dat_basic.csv")) |> 
  filter(wage_per_hour > 700, wage_per_hour < 10000)

df_cov <-
  read_csv(here::here("/masters_thesis/data/panel/dat_panel_cov.csv"))

# 1. まず、元データの確認
# print("元のd_term_fixedの分布:")
# table(df_cov$d_term_fixed, useNA = "ifany")

# Prepare data for analysis
df_full <- df_basic |> 
  left_join(df_cov, by = c("ID", "year"))|> 
  mutate(age_10s = age %/% 10,
         d_position = if_else(position <= 7, 1, 0),
         small_firm = if_else(firm_size <= 7, 1, 0),
         d_term_fixed = if_else(d_term_fixed == 1, 1, 0), #期間が定められていれば１
         d_contract_change = if_else(d_reg_nonreg == 1 | q_nonreg_reg == 1,
                                     1, 0),
         relativetime = year - year_entry_current - 5,
         coarse_industry = as.factor(coarse_industry),
         sex = as.factor(sex),
         edu_cg = as.factor(edu_cg)
         ) 
# table(df_full$d_term_fixed)

# フィルタリング
# df_full_corrected <- df_full |>
#   group_by(ID) |>
#   mutate(
#     has_fixed_at_minus5 = any(relativetime == -5 & d_term_fixed == 1, na.rm = TRUE)
#   ) |>
#   filter(has_fixed_at_minus5) |>
#   select(-has_fixed_at_minus5)

# -5のデータがそもそも存在しない人もいる

# -5年の時点で契約雇用期間のあるIDを特定
df_full_corrected <- df_full |>
   group_by(ID) |>
   filter(any(relativetime == -5 & d_term_fixed == 1)) |> 
            filter(any(relativetime == -4 & d_term_fixed == 1)) |> 
                     filter(any(relativetime == -3 & d_term_fixed == 1)) |> 
                              filter(any(relativetime == -2 & d_term_fixed == 1)) |> 
                                       filter(any(relativetime == -1 & d_term_fixed == 1))

# df_check <- df_full_corrected |>
#   filter(relativetime == -5)
# table(df_check$d_term_fixed)

df_full <- df_full_corrected |>
  mutate(
    treat = case_when(
      year_entry_current >= 2013 & year_entry_current <= 2017 ~ 1,
      year_entry_current <= 2012 | year_entry_current >= 2018 ~ 0   
    ),
    post_treat = case_when(
      year_entry_current == 2013 & year >= 2018 ~ 1,
      year_entry_current == 2014 & year >= 2019 ~ 1,
      year_entry_current == 2015 & year >= 2020 ~ 1,
      year_entry_current == 2016 & year >= 2021 ~ 1,
      year_entry_current == 2017 & year >= 2022 ~ 1,
      TRUE ~ 0)) |> 
  mutate(eventtime = if_else(treat == 1, relativetime, 0))

# 最初に介入を受ける年を特定
df_full <- 
df_full |> 
  group_by(ID) |> 
  mutate(first.treat = first(year[post_treat == 1], na_rm = T)) |> 
  mutate(first.treat = replace_na(first.treat, 0),
         d_term_fixed = 1- d_term_fixed) |>
  filter(age <= 60) |> 
  ungroup()

df_notyet <- 
  df_full |> 
  filter(year_entry_current >= 2013)

df_lt <-
  df_full |> 
  filter(year_entry_current <= 2017 & year_entry_current >= 2013)

```

## Sample Size
```{r, echo=FALSE}
sample_sizes <- df_notyet %>%
  distinct(ID, first.treat) %>%
  group_by(first.treat) %>%
  summarise(n = n()) %>%
  arrange(first.treat)

datatable(sample_sizes)

```

## Transition of the Outcome
```{r transition, echo=FALSE}

ft <- df_full %>%
  filter(abs(relativetime) <= 7) %>%  
  group_by(relativetime, treat) %>%
  summarise(
    mean_outcome = mean(d_term_fixed, na.rm = TRUE),
    se = sd(d_term_fixed, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  ) %>%
  ggplot(aes(x = relativetime, y = mean_outcome, color = factor(treat))) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_point() +
  geom_line() +
  # geom_ribbon(
  #   aes(ymin = mean_outcome - 1.96*se, 
  #       ymax = mean_outcome + 1.96*se,
  #       fill = factor(treat)),
  #   alpha = 0.2,
  #   color = NA
  # ) +
  scale_color_manual(
    values = c("0" = "blue", "1" = "red"),
    labels = c("Control", "Treated"),
    name = "Group"
  ) +
  # scale_fill_manual(
  #   values = c("0" = "blue", "1" = "red"),
  #   labels = c("Control", "Treated"),
  #   name = "Group"
  # ) +
  labs(
    x = "Time Relative to Treatment",
    y = "Proportion of Indefinite-term Contract",
    title = "Trends in Fixed Term Contracts",
    subtitle = "Vertical line indicates treatment timing"
  ) +
  theme_minimal()

ft


##賃金の推移プロット
t2 <- df_full %>%
  group_by(relativetime, treat) %>%
  summarise(
    mean_outcome = mean(logwage, na.rm = TRUE),
    se = sd(d_term_fixed, na.rm = TRUE) / sqrt(n()),
    .groups = 'drop'
  ) %>%
  filter(relativetime <= 5) |> 
  ggplot(aes(x = relativetime, y = mean_outcome, color = factor(treat))) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_point() +
  geom_line() +
  # geom_ribbon(
  #   aes(ymin = mean_outcome - 1.96*se, 
  #       ymax = mean_outcome + 1.96*se,
  #       fill = factor(treat)),
  #   alpha = 0.2,
  #   color = NA
  # ) +
  scale_color_manual(
    values = c("0" = "blue", "1" = "red"),
    labels = c("Control", "Treated"),
    name = "Group"
  ) +
  # scale_fill_manual(
  #   values = c("0" = "blue", "1" = "red"),
  #   labels = c("Control", "Treated"),
  #   name = "Group"
  # ) +
  labs(
    x = "Time Relative to Treatment",
    y = "Log Wage Growth",
    title = "Trends in Log Wage Growth",
    subtitle = "Vertical line indicates treatment timing"
  ) +
  theme_minimal()

t2

```

## DID analysis
```{r CS, echo=FALSE, warning=FALSE, message=FALSE}

outcomes <- 
  df_full |> 
  select(d_term_fixed, 
             logwage,
         hourly_wage,
         regular) |> 
  names() |> 
    purrr::set_names()

# Only not yet with universal base period
list_results4 <- map(outcomes, function(y) {
  att_gt(
    yname = y,
    gname = "first.treat",
    idname = "ID",
    tname = "year",
    control_group = "notyettreated",
    base_period = "universal",
    xformla = ~1,
    data = df_lt,
    allow_unbalanced_panel = TRUE,
    est_method = "dr"
  )
})

list_aggresults4 <- map(list_results4, function(result) {
  aggte(result, type = "dynamic", na.rm = TRUE)
})

# Include never treated with universal base period
list_results5 <- map(outcomes, function(y) {
  att_gt(
    yname = y,
    gname = "first.treat",
    idname = "ID",
    tname = "year",
    control_group = "notyettreated",
        base_period = "universal",
    xformla = ~1,
    data = df_notyet,
    allow_unbalanced_panel = TRUE,
    est_method = "dr"
  )
})

list_aggresults5 <- map(list_results5, function(result) {
  aggte(result, type = "dynamic", na.rm = TRUE)
})


# ONly never treated with universal base period
list_results6 <- map(outcomes, function(y) {
  att_gt(
    yname = y,
    gname = "first.treat",
    idname = "ID",
    tname = "year",
    control_group = "nevertreated",
        base_period = "universal",
    xformla = ~1,
    data = df_notyet,
    allow_unbalanced_panel = TRUE,
    est_method = "dr"
  )
})

list_aggresults6 <- map(list_results6, function(result) {
  aggte(result, type = "dynamic", na.rm = TRUE)
})

# Only not yet with universal base period and with age and educ
list_results7 <- map(outcomes, function(y) {
  att_gt(
    yname = y,
    gname = "first.treat",
    idname = "ID",
    tname = "year",
    control_group = "notyettreated",
    base_period = "universal",
    xformla = ~age + edu_cg,
    data = df_lt,
    allow_unbalanced_panel = TRUE,
    est_method = "reg"
  )
})

list_aggresults7 <- map(list_results4, function(result) {
  aggte(result, type = "dynamic", na.rm = TRUE)
})

```


# Results with universal base period {.tabset}

## Only Not Yet Treated as a Comparison

### Group-Time Treatment Effect {.tabset}
```{r gt4,echo=FALSE, results='asis', message=FALSE, warning=FALSE, fig.height=20, fig.width=12}

section_title <- 
  c("雇用に期間がある割合(上が無期)",
    "Log wage",
    "時給(円)",
    "「正規雇用」の割合")

list_CSplots4 <- map(list_results4, function(result) {
  plot <- ggdid(result)
  })

## output
walk2(list_CSplots4, section_title, function(plot, title) {
  cat("#### ", title, " \n")
  print(plot)
  cat(" \n\n")
})
```

### Event study Results {.tabset}

```{r plot4, echo=FALSE, results='asis', warning=FALSE, fig.width=8}

list_aggplots4 <- map(list_aggresults4, function(aggte_result) {
  ggdid(aggte_result, xgap = 1)
})

walk2(list_aggplots4, section_title, function(plot, title) {
  cat("#### ", title, " \n")
  print(plot)
  cat(" \n\n")
})

```

## Not Yet Treated + Never Treated as a Comparison

### Group-Time Treatment Effect {.tabset}
```{r gt5,echo=FALSE, results='asis', message=FALSE, warning=FALSE, fig.height=20, fig.width=12}

list_CSplots5 <- map(list_results5, function(result) {
  plot <- ggdid(result)
  })

## output
walk2(list_CSplots5, section_title, function(plot, title) {
  cat("#### ", title, " \n")
  print(plot)
  cat(" \n\n")
})
```

### Event study Results {.tabset}

```{r plot5, echo=FALSE, results='asis', warning=FALSE, fig.width=15}

list_aggplots5 <- map(list_aggresults5, function(aggte_result) {
  ggdid(aggte_result, xgap = 1)
})

walk2(list_aggplots5, section_title, function(plot, title) {
  cat("#### ", title, " \n")
  print(plot)
  cat(" \n\n")
})

```

## Only Never Treated as a Comparison

### Group-Time Treatment Effect {.tabset}
```{r gt6,echo=FALSE, results='asis', message=FALSE, warning=FALSE, fig.height=20, fig.width=12}

list_CSplots6 <- map(list_results6, function(result) {
  plot <- ggdid(result)
  })

## output
walk2(list_CSplots6, section_title, function(plot, title) {
  cat("#### ", title, " \n")
  print(plot)
  cat(" \n\n")
})
```

### Event study Results {.tabset}

```{r plot6, echo=FALSE, results='asis', warning=FALSE, fig.width=15}

list_aggplots6 <- map(list_aggresults6, function(aggte_result) {
  ggdid(aggte_result, xgap = 1)
})

walk2(list_aggplots6, section_title, function(plot, title) {
  cat("#### ", title, " \n")
  print(plot)
  cat(" \n\n")
})

```


## Not yet with cov

### Group-Time Treatment Effect {.tabset}
```{r gt7,echo=FALSE, results='asis', message=FALSE, warning=FALSE, fig.height=20, fig.width=12}

list_CSplots7 <- map(list_results7, function(result) {
  plot <- ggdid(result)
  })

## output
walk2(list_CSplots7, section_title, function(plot, title) {
  cat("#### ", title, " \n")
  print(plot)
  cat(" \n\n")
})
```

### Event study Results {.tabset}

```{r plot7, echo=FALSE, results='asis', warning=FALSE, fig.width=15}

list_aggplots7 <- map(list_aggresults7, function(aggte_result) {
  ggdid(aggte_result, xgap = 1)
})

walk2(list_aggplots7, section_title, function(plot, title) {
  cat("#### ", title, " \n")
  print(plot)
  cat(" \n\n")
})

```


# Interaction term (Martins(2021)) and Sun & Abraham (2020) {.tabset}

$$
\begin{aligned}
Y_{it} =  \sum_{r \neq -1} \beta_r \mathbb{I} (t =  r) \times Treat_i + \alpha_i + \lambda_t + \epsilon_{it}
\end{aligned}
$$

## Indefinite-Term Contract
```{r, echo=FALSE, message=FALSE, fig.height=8}

reg0 <- 
  feols(d_term_fixed ~ i(eventtime, treat, ref = -1) | ID + year,
        cluster = ~ID,
        data = df_lt)

reg_0_2 <-
  feols(d_term_fixed ~ sunab(first.treat, year) | ID + year,
        cluster = ~ID,
        data = df_lt)

iplot(list(reg0, reg_0_2), sep = 0.2, ref.line = -1,
      xlab = 'Time to treatment',
      ylab = "Proportion of workers with permanent contract")
legend("bottomleft", col = c(1, 2), pch = c(20, 17), 
       legend = c("Interaction", "Sun & Abraham"))

```

## Logwage
```{r, echo=FALSE, message=FALSE, fig.height=8}

reg1 <- 
  feols(logwage ~ i(eventtime, treat, ref = -1) | ID + year,
        cluster = ~ID,
        data = df_lt)

reg_1_2 <-
  feols(logwage ~ sunab(first.treat, year) | ID + year,
        cluster = ~ID,
        data = df_lt)

iplot(list(reg1, reg_1_2), sep = 0.2, ref.line = -1,
      xlab = 'Time to treatment',
      ylab = "log wage")
legend("bottomleft", col = c(1, 2), pch = c(20, 17), 
       legend = c("Interaction", "Sun & Abraham"))

```

## wage
```{r, echo=FALSE, message=FALSE, fig.height=8}

reg2 <- 
  feols(hourly_wage ~ i(eventtime, treat, ref = -1) | ID + year,
        cluster = ~ID,
        data = df_lt)

reg_2_2 <-
  feols(hourly_wage ~ sunab(first.treat, year) | ID + year,
        cluster = ~ID,
        data = df_lt)

iplot(list(reg2, reg_2_2), sep = 0.2, ref.line = -1,
      xlab = 'Time to treatment',
      ylab = "Hourly wage")
legend("bottomleft", col = c(1, 2), pch = c(20, 17), 
       legend = c("Interaction", "Sun & Abraham"))

```

## Regular
```{r, echo=FALSE, message=FALSE, fig.height=8}

reg3 <- 
  feols(regular ~ i(eventtime, treat, ref = -1) | ID + year,
        cluster = ~ID,
        data = df_lt)

reg_3_2 <-
  feols(regular~ sunab(first.treat, year) | ID + year,
        cluster = ~ID,
        data = df_lt)

iplot(list(reg3, reg_3_2), sep = 0.2, ref.line = -1,
      xlab = 'Time to treatment',
      ylab = "Proportion of workers with 'regular' contract")
legend("bottomleft", col = c(1, 2), pch = c(20, 17), 
       legend = c("Interaction", "Sun & Abraham"))

```


# TWFE event study (Miller 2023){ .tabset}

$$
\begin{aligned}
Y_{it} = \alpha_i + \lambda_t + \sum_{r \neq -1} \beta_r \mathbb{I} (t =  r) + \epsilon_{it}
\end{aligned}
$$

```{r, echo=FALSE}
## Setting

df_twfe <- df_lt %>%
  mutate(
    time_til = year - first.treat,
    lead1 = case_when(time_til == -1 ~ 1, TRUE ~ 0),
    lead2 = case_when(time_til == -2 ~ 1, TRUE ~ 0),
    lead3 = case_when(time_til == -3 ~ 1, TRUE ~ 0),
    lead4 = case_when(time_til == -4 ~ 1, TRUE ~ 0),
    lead5 = case_when(time_til == -5 ~ 1, TRUE ~ 0),
    lead6 = case_when(time_til == -6 ~ 1, TRUE ~ 0),
    lead7 = case_when(time_til == -7 ~ 1, TRUE ~ 0),
    
    lag0 = case_when(time_til == 0 ~ 1, TRUE ~ 0),
    lag1 = case_when(time_til == 1 ~ 1, TRUE ~ 0),
    lag2 = case_when(time_til == 2 ~ 1, TRUE ~ 0),
    lag3 = case_when(time_til == 3 ~ 1, TRUE ~ 0),
    lag4 = case_when(time_til == 4 ~ 1, TRUE ~ 0),
    lag5 = case_when(time_til == 5 ~ 1, TRUE ~ 0)
  )

event_study_formula <- as.formula(
  paste("d_term_fixed ~ + ",
        paste(
          paste(paste("lead", 1:7, sep = ""), collapse = " + "),
          paste(paste("lag", 1:5, sep = ""), collapse = " + "), sep = " + "),
        "| year + ID | 0 | ID"
  ),
)

event_study_reg <- felm(event_study_formula, data = df_twfe)
# summary(event_study_reg)

```

## Indefinite-Term Contract
```{r, echo=FALSE, message=FALSE}
# order of the coefficients for the plot
plot_order <- c("lead7", 
                "lead6", "lead5", "lead4", "lead3", 
                "lead2", "lead1", "lag1", 
                "lag2", "lag3", "lag4", "lag5")

# grab the clustered standard errors
# and average coefficient estimates
# from the regression, label them accordingly
# add a zero'th lag for plotting purposes
leadslags_plot <- tibble(
  sd = c(event_study_reg$cse[plot_order], 0),
  mean = c(coef(event_study_reg)[plot_order], 0),
  label = c(-7,-6, -5, -4, -3, -2, -1, 1,2,3,4,5, 0)
)

# This version has a point-range at each
# estimated lead or lag
# comes down to stylistic preference at the
# end of the day!
leadslags_plot %>%
  ggplot(aes(x = label, y = mean,
             ymin = mean-1.96*sd, 
             ymax = mean+1.96*sd)) +
  geom_pointrange() +
  theme_minimal() +
  xlab("Relative year") +
  ylab("Proportion of workers with permanent contract") +
  geom_hline(yintercept = 0,
             linetype = "dashed") +
  geom_vline(xintercept = 0,
             linetype = "dashed")
  
```

## logWage
```{r, echo=FALSE, message=FALSE}

event_study_formula2 <- as.formula(
  paste("logwage ~ + ",
        paste(
          paste(paste("lead", 1:7, sep = ""), collapse = " + "),
          paste(paste("lag", 1:5, sep = ""), collapse = " + "), sep = " + "),
        "| year + ID| 0 | ID"
  ),
)

event_study_reg2 <- felm(event_study_formula2, data = df_twfe)
# summary(event_study_reg2)

```


```{r, echo=FALSE}
leadslags_plot2 <- tibble(
  sd = c(event_study_reg2$cse[plot_order], 0),
  mean = c(coef(event_study_reg2)[plot_order], 0),
  label = c(-7,-6, -5, -4, -3, -2, -1, 1,2,3,4,5, 0)
)

# This version has a point-range at each
# estimated lead or lag
# comes down to stylistic preference at the
# end of the day!
leadslags_plot2 %>%
  ggplot(aes(x = label, y = mean,
             ymin = mean-1.96*sd, 
             ymax = mean+1.96*sd)) +
  geom_pointrange() +
  theme_minimal() +
  xlab("Relative year") +
  ylab("Log wage") +
  geom_hline(yintercept = 0,
             linetype = "dashed") +
  geom_vline(xintercept = 0,
             linetype = "dashed")

```

## Wage
```{r, echo=FALSE, message=FALSE}

event_study_formula3 <- as.formula(
  paste("hourly_wage ~ + ",
        paste(
          paste(paste("lead", 1:7, sep = ""), collapse = " + "),
          paste(paste("lag", 1:5, sep = ""), collapse = " + "), sep = " + "),
        "| year + ID| 0 | ID"
  ),
)

event_study_reg3 <- felm(event_study_formula3, data = df_twfe)
# summary(event_study_reg2)

```


```{r, echo=FALSE}
leadslags_plot3 <- tibble(
  sd = c(event_study_reg3$cse[plot_order], 0),
  mean = c(coef(event_study_reg3)[plot_order], 0),
  label = c(-7,-6, -5, -4, -3, -2, -1, 1,2,3,4,5, 0)
)

# This version has a point-range at each
# estimated lead or lag
# comes down to stylistic preference at the
# end of the day!
leadslags_plot3 %>%
  ggplot(aes(x = label, y = mean,
             ymin = mean-1.96*sd, 
             ymax = mean+1.96*sd)) +
  geom_pointrange() +
  theme_minimal() +
  xlab("Relative year") +
  ylab("Wage") +
  geom_hline(yintercept = 0,
             linetype = "dashed") +
  geom_vline(xintercept = 0,
             linetype = "dashed")

```

## Regular
```{r, echo=FALSE, message=FALSE}

event_study_formula4 <- as.formula(
  paste("regular ~ + ",
        paste(
          paste(paste("lead", 1:7, sep = ""), collapse = " + "),
          paste(paste("lag", 1:5, sep = ""), collapse = " + "), sep = " + "),
        "| year + ID| 0 | ID"
  ),
)

event_study_reg4 <- felm(event_study_formula4, data = df_twfe)
# summary(event_study_reg2)

```


```{r, echo=FALSE}
leadslags_plot4 <- tibble(
  sd = c(event_study_reg4$cse[plot_order], 0),
  mean = c(coef(event_study_reg4)[plot_order], 0),
  label = c(-7,-6, -5, -4, -3, -2, -1, 1,2,3,4,5, 0)
)

# This version has a point-range at each
# estimated lead or lag
# comes down to stylistic preference at the
# end of the day!
leadslags_plot4 %>%
  ggplot(aes(x = label, y = mean,
             ymin = mean-1.96*sd, 
             ymax = mean+1.96*sd)) +
  geom_pointrange() +
  theme_minimal() +
  xlab("Relative year") +
  ylab("Proportion of workers woth 'regular' contract") +
  geom_hline(yintercept = 0,
             linetype = "dashed") +
  geom_vline(xintercept = 0,
             linetype = "dashed")

```