---
title: "Basic discriptive statistics"
author: "Kyohei Sato"
date: "2024-09-09"
output: html_document
---

```{r setup, include=FALSE}
pacman::p_load(tidyverse, here, DT, outliers, ggridges)

dat_basic <- 
  read_csv(here::here("/masters_thesis/data/panel/dat_basic.csv"))

## Outliers
dat_basic <- 
  dat_basic |> 
  filter(wage_per_hour > 700, wage_per_hour < 10000)

```


## Contarct Type

```{r CT, echo=FALSE, message=FALSE}

hist1 <- ggplot(dat_basic, aes(x = contract_type))+
  geom_histogram() +
  scale_x_continuous(breaks = seq(0,6,1))

hist1

```

## Education {.tabset}

### Regular
```{r Educ reg, echo=FALSE, message=FALSE}

dat_regular <- 
  dat_basic |> 
  filter(regular == 1)

hist2 <- ggplot(dat_regular, aes(x = educ))+
  geom_histogram() +
  scale_x_continuous(breaks = seq(0,8,1))

hist2

```

### Part-Time
```{r educ PT, echo=FALSE}

dat_pt <- 
  dat_basic |> 
  filter(part_time == 1)

hist3 <- ggplot(dat_pt, aes(x = educ))+
  geom_histogram() +
  scale_x_continuous(breaks = seq(0,8,1))

hist3

```

### Dispatched
```{r educ disp, echo=FALSE}

dat_disp <- 
  dat_basic |> 
  filter(dispatched == 1)

hist4 <- ggplot(dat_disp, aes(x = educ))+
  geom_histogram() +
  scale_x_continuous(breaks = seq(0,8,1))

hist4

```

### Fixed-term
```{r FT, echo=FALSE}

dat_ft <- 
  dat_basic |> 
  filter(fixed_term == 1)

hist5 <- ggplot(dat_ft, aes(x = educ))+
  geom_histogram() +
  scale_x_continuous(breaks = seq(0,8,1))

hist5
```

### Shokutaku
```{r sho, echo=FALSE}
dat_sho <- 
  dat_basic |> 
  filter(shokutaku == 1)

hist6 <- ggplot(dat_sho, aes(x = educ))+
  geom_histogram() +
  scale_x_continuous(breaks = seq(0,8,1))

hist6
```


## Wage per hour {.tabset}
How can we deal with outliers?

### 4 in 1
```{r wage 4 in 1, echo=FALSE}
p <- ggplot(data = dat_basic,
mapping = aes(x = logwage, y = factor(contract_type))) +
geom_density_ridges() +
labs(x = "log wage", y = NULL)

p
```


### Regular
```{r regwage, echo=FALSE, message=FALSE}
## too long tail

hist7 <- ggplot(dat_regular, aes(x = logwage))+
  geom_histogram(bins = 50)
  

hist7

```

### Part-Time
```{r ptwage, echo=FALSE}
## too long tail

hist8 <- ggplot(dat_pt, aes(x = logwage))+
  geom_histogram(bins = 50)
  

hist8

```

### Dispatched
```{r dispwage, echo=FALSE}
## too long tail

hist9 <- ggplot(dat_disp, aes(x = logwage))+
  geom_histogram(bins = 50)
  

hist9

```

### Fixed-Time
```{r ftwage, echo=FALSE}
## too long tail

hist10 <- ggplot(dat_ft, aes(x = logwage))+
  geom_histogram(bins = 50)
  

hist10

```

### Shokutaku
```{r showage, echo=FALSE}
## too long tail

hist11 <- ggplot(dat_sho, aes(x = logwage))+
  geom_histogram(bins = 50)
  
hist11

```

## OJT {.tabset}

### ALL
```{r OJT1, echo=FALSE, message=FALSE}

dat_train <- 
  dat_basic |> 
  group_by(contract_type, year) |> 
  summarise(mean_OJT = mean(d_OJT)) |> 
  filter(contract_type < 6)

line_train <- ggplot(dat_train, aes(x = year, y = mean_OJT, color = as.factor(contract_type))) +
  geom_line() + 
  geom_point() +
  labs(x = "Year",
       y = "Proportion of OJT taker",
       color = "Contract Type") + 
  theme_minimal()  

line_train

```

### Regular vs Dispatched
```{r OJT2, echo=FALSE}

dat_dif_OJT <- 
  dat_train |>
  filter(contract_type %in% c(1,3)) |> 
  pivot_wider(names_from = contract_type, values_from = mean_OJT,
              names_prefix = "contract_type_") |> 
  mutate(OJT_diff = contract_type_1 - contract_type_3, type = "Regular vs Dispatched")

line_OJT_diff1 <- ggplot(dat_dif_OJT, aes(x = year, y = OJT_diff)) +
  geom_line(color = "blue") + 
  geom_point() +
  labs(x = "Year",
       y = "Difference in proportion of OJT taker",
       color = "Difference in Propottion of OJT taker b/w regular and dispatched") + 
  geom_vline(xintercept  = 2020, color = "red", linetype = "dashed") +
  theme_minimal()  

line_OJT_diff1

```

### Part-Time vs Dispatched
```{r OJT3, echo=FALSE}

dat_dif_OJT2 <- 
  dat_train |>
  filter(contract_type %in% c(2,3)) |> 
  pivot_wider(names_from = contract_type, values_from = mean_OJT,
              names_prefix = "contract_type_") |> 
  mutate(OJT_diff = contract_type_2 - contract_type_3, type = "Part-time vs Dispatched")

line_OJT_diff2 <- ggplot(dat_dif_OJT2, aes(x = year, y = OJT_diff)) +
  geom_line(color = "blue") + 
  geom_point() +
  labs(x = "Year",
       y = "Difference in proportion of OJT taker",
       color = "Difference in Propottion of OJT taker b/w part-time and dispatched") + 
  geom_vline(xintercept  = 2020, color = "red", linetype = "dashed") +
  theme_minimal()  

line_OJT_diff2

```

### Fixed-term vs Dispatched
```{r OJT4, echo=FALSE}

dat_dif_OJT3 <- 
  dat_train |>
  filter(contract_type %in% c(4,3)) |> 
  pivot_wider(names_from = contract_type, values_from = mean_OJT,
              names_prefix = "contract_type_") |> 
  mutate(OJT_diff = contract_type_4 - contract_type_3, type = "Fixed-tern vs Dispatched")

line_OJT_diff3 <- ggplot(dat_dif_OJT3, aes(x = year, y = OJT_diff)) +
  geom_line(color = "blue") + 
  geom_point() +
  labs(x = "Year",
       y = "Difference in proportion of OJT taker",
       color = "Difference in Propottion of OJT taker b/w fixed-term and dispatched") + 
  geom_vline(xintercept  = 2020, color = "red", linetype = "dashed") +
  theme_minimal()  

line_OJT_diff3

```

### Shokutaku vs Dispatched
```{r OJT5, echo=FALSE}

dat_dif_OJT4 <- 
  dat_train |>
  filter(contract_type %in% c(5,3)) |> 
  pivot_wider(names_from = contract_type, values_from = mean_OJT,
              names_prefix = "contract_type_") |> 
  mutate(OJT_diff = contract_type_5 - contract_type_3, type = "Shokutaku vs Dispatched")

line_OJT_diff4 <- ggplot(dat_dif_OJT4, aes(x = year, y = OJT_diff)) +
  geom_line(color = "blue") + 
  geom_point() +
  labs(x = "Year",
       y = "Difference in proportion of OJT taker",
       color = "Difference in Propottion of OJT taker b/w Shokutaku and dispatched") + 
  geom_vline(xintercept  = 2020, color = "red", linetype = "dashed") +
  theme_minimal()  

line_OJT_diff4

```

### Difference in OJT taker (4 in 1)
```{r OJT6, echo=FALSE}

combined_data <- bind_rows(dat_dif_OJT, dat_dif_OJT2, dat_dif_OJT3, dat_dif_OJT4) |> 
  select(year, OJT_diff, type)

difference_in_OJT_growth <- 
  ggplot(combined_data, aes(x = year, y = OJT_diff, color = type)) +
  geom_line() + 
  geom_point() +
  geom_vline(xintercept = 2020, color = "red", linetype = "dashed") +
  labs(title = "OJTの経年変化",
       x = "Year",
       y = "Difference in proportion of OJT takers",
       color = "Comparison") +  
  theme_minimal()

difference_in_OJT_growth 

```


## OFF_JT {.tabset}

### ALL
```{r OFF1, echo=FALSE, message=FALSE}

dat_OFF <- 
  dat_basic |> 
  group_by(contract_type, year) |> 
  summarise(mean_OFF = mean(d_OFF_JT)) |> 
  filter(contract_type < 6)

line_OFF <- ggplot(dat_OFF, aes(x = year, y = mean_OFF, color = as.factor(contract_type))) +
  geom_line() + 
  geom_point() +
  labs(x = "Year",
       y = "Proportion of OFF-JT taker",
       color = "Contract Type") + 
  theme_minimal()  

line_OFF

```

### Regular vs Dispatched
```{r OFF2, echo=FALSE}

dat_dif_OFF <- 
  dat_OFF |>
  filter(contract_type %in% c(1,3)) |> 
  pivot_wider(names_from = contract_type, values_from = mean_OFF,
              names_prefix = "contract_type_") |> 
  mutate(OFF_diff = contract_type_1 - contract_type_3, type = "Regular vs Dispatched")

line_OFF_diff1 <- ggplot(dat_dif_OFF, aes(x = year, y = OFF_diff)) +
  geom_line(color = "blue") + 
  geom_point() +
  labs(x = "Year",
       y = "Difference in proportion of OFF-JT taker",
       color = "Difference in Propottion of OFF-JT taker b/w regular and dispatched") + 
  geom_vline(xintercept  = 2020, color = "red", linetype = "dashed") +
  theme_minimal()  

line_OJT_diff1

```

### Part-Time vs Dispatched
```{r OFF3, echo=FALSE}

dat_dif_OFF2 <- 
  dat_OFF |>
  filter(contract_type %in% c(2,3)) |> 
  pivot_wider(names_from = contract_type, values_from = mean_OFF,
              names_prefix = "contract_type_") |> 
  mutate(OFF_diff = contract_type_2 - contract_type_3, type = "Part-time vs Dispatched")

line_OFF_diff2 <- ggplot(dat_dif_OFF2, aes(x = year, y = OFF_diff)) +
  geom_line(color = "blue") + 
  geom_point() +
  labs(x = "Year",
       y = "Difference in proportion of OFF-JT taker",
       color = "Difference in Propottion of OFF-JT taker b/w part-time and dispatched") + 
  geom_vline(xintercept  = 2020, color = "red", linetype = "dashed") +
  theme_minimal()  

line_OFF_diff2

```

### Fixed-term vs Dispatched
```{r OFF4, echo=FALSE}

dat_dif_OFF3 <- 
  dat_OFF |>
  filter(contract_type %in% c(4,3)) |> 
  pivot_wider(names_from = contract_type, values_from = mean_OFF,
              names_prefix = "contract_type_") |> 
  mutate(OFF_diff = contract_type_4 - contract_type_3, type = "Fixed-tern vs Dispatched")

line_OFF_diff3 <- ggplot(dat_dif_OFF3, aes(x = year, y = OFF_diff)) +
  geom_line(color = "blue") + 
  geom_point() +
  labs(x = "Year",
       y = "Difference in proportion of OFF-JT taker",
       color = "Difference in Propottion of OFF-JT taker b/w fixed-term and dispatched") + 
  geom_vline(xintercept  = 2020, color = "red", linetype = "dashed") +
  theme_minimal()  

line_OFF_diff3

```

### Shokutaku vs Dispatched
```{r OFF5, echo=FALSE}

dat_dif_OFF4 <- 
  dat_OFF |>
  filter(contract_type %in% c(5,3)) |> 
  pivot_wider(names_from = contract_type, values_from = mean_OFF,
              names_prefix = "contract_type_") |> 
  mutate(OFF_diff = contract_type_5 - contract_type_3, type = "Shokutaku vs Dispatched")

line_OFF_diff4 <- ggplot(dat_dif_OFF4, aes(x = year, y = OFF_diff)) +
  geom_line(color = "blue") + 
  geom_point() +
  labs(x = "Year",
       y = "Difference in proportion of OFF-JT taker",
       color = "Difference in Propottion of OFF-JT taker b/w Shokutaku and dispatched") + 
  geom_vline(xintercept  = 2020, color = "red", linetype = "dashed") +
  theme_minimal()  

line_OFF_diff4

```

### Difference in OFF-JT taker (4 in 1)
```{r OFF6, echo=FALSE}

combined_data <- bind_rows(dat_dif_OFF, dat_dif_OFF2, dat_dif_OFF3, dat_dif_OFF4) |> 
  select(year, OFF_diff, type)

difference_in_OFF_growth <- 
  ggplot(combined_data, aes(x = year, y = OFF_diff, color = type)) +
  geom_line() + 
  geom_point() +
  geom_vline(xintercept = 2020, color = "red", linetype = "dashed") +
  labs(title = "OFF-JTの経年変化",
       x = "Year",
       y = "Difference in proportion of OFF-JT takers",
       color = "Comparison") +  
  theme_minimal()

difference_in_OFF_growth 

```

## Change by Year{.tabset}

### wage change by contract type
```{r change in wage, echo=FALSE, message=FALSE}

dat_wage <- 
  dat_basic |> 
  group_by(contract_type, year) |>
  summarise(meanwage = mean(logwage, na.rm = TRUE)) |> 
  filter(contract_type < 6) 
  
line_wage <- ggplot(dat_wage, aes(x = year, y = meanwage, color = as.factor(contract_type))) +
  geom_line() + 
  geom_point() +
  labs(x = "Year",
       y = "Mean Wage (log)",
       color = "Contract Type") + 
  theme_minimal()  

line_wage

```

### Regular vs Dispatched
```{r diff in wage r and d, echo=FALSE}
  
dat_dif <- 
  dat_wage |>
  filter(contract_type %in% c(1,3)) |> 
  pivot_wider(names_from = contract_type, values_from = meanwage,
              names_prefix = "contract_type_") |> 
  mutate(wage_diff = contract_type_1 - contract_type_3, type = "Regular vs Dispatched")

line_wage_diff1 <- ggplot(dat_dif, aes(x = year, y = wage_diff)) +
  geom_line(color = "blue") + 
  geom_point() +
  labs(x = "Year",
       y = "Difference in Mean Wage (log)",
       color = "Wage Difference b/w regular and dispatched") + 
  geom_vline(xintercept  = 2020, color = "red", linetype = "dashed") +
  theme_minimal()  

line_wage_diff1

```

### Part-time vs Dispatched
```{r diff in wage p and d, echo=FALSE}
  
dat_dif2 <- 
  dat_wage |>
  filter(contract_type %in% c(2,3)) |> 
  pivot_wider(names_from = contract_type, values_from = meanwage,
              names_prefix = "contract_type_") |> 
  mutate(wage_diff = contract_type_2 - contract_type_3, type = "Part-time vs Dispatched")

line_wage_diff2 <- ggplot(dat_dif2, aes(x = year, y = wage_diff)) +
  geom_line(color = "blue") + 
  geom_point() +
  labs(x = "Year",
       y = "Difference in Mean Wage (log)",
       color = "Wage Difference b/w part-time and dispatched") + 
  geom_vline(xintercept  = 2020, color = "red", linetype = "dashed") +
  theme_minimal()  

line_wage_diff2

```

### Fixed term vs Dispatched
```{r diff in wage f and d, echo=FALSE}
  
dat_dif3 <- 
  dat_wage |>
  filter(contract_type %in% c(3, 4)) |> 
  pivot_wider(names_from = contract_type, values_from = meanwage,
              names_prefix = "contract_type_") |> 
  mutate(wage_diff = contract_type_4 - contract_type_3, type = "Fixed-term vs Dispatched")

line_wage_diff3 <- ggplot(dat_dif3, aes(x = year, y = wage_diff)) +
  geom_line(color = "blue") + 
  geom_point() +
  labs(x = "Year",
       y = "Difference in Mean Wage (log)",
       color = "Wage Difference b/w fixed-term and dispatched") + 
  geom_vline(xintercept  = 2020, color = "red", linetype = "dashed") +
  theme_minimal()  

line_wage_diff3
```

### Shokutaku vs Dispatched
```{r diff in wage s and d, echo=FALSE}
  
dat_dif4 <- 
  dat_wage |>
  filter(contract_type %in% c(3, 5)) |> 
  pivot_wider(names_from = contract_type, values_from = meanwage,
              names_prefix = "contract_type_") |> 
  mutate(wage_diff = contract_type_5 - contract_type_3, type = "Shokutaku vs Dispatched")

line_wage_diff4 <- ggplot(dat_dif4, aes(x = year, y = wage_diff)) +
  geom_line(color = "blue") + 
  geom_point() +
  labs(x = "Year",
       y = "Difference in Mean Wage (log)",
       color = "Wage Difference b/w shokutaku and dispatched") + 
  geom_vline(xintercept  = 2020, color = "red", linetype = "dashed") +
  theme_minimal()  

line_wage_diff4
```

### Difference in wage growth (4 in 1)
```{r diff in wage growth, echo=FALSE}
  
combined_data <- bind_rows(dat_dif, dat_dif2, dat_dif3, dat_dif4) |> 
  select(year, wage_diff, type)

difference_in_wage_growth <- 
  ggplot(combined_data, aes(x = year, y = wage_diff, color = type)) +
  geom_line() + 
  geom_point() +
  geom_vline(xintercept = 2020, color = "red", linetype = "dashed") +
  labs(title = "賃金差の経年変化",
       x = "Year",
       y = "Wage Difference",
       color = "Comparison") +  
  theme_minimal()

difference_in_wage_growth 
```