---
title: "Turn to Permanent Contract, Constructiong Cohort, Discriptive Statistics"
author: "Kyohei Sato"
date: "2024-10-16"
output: html_document
---

```{r setup, include=FALSE}
# Install packages

if (!require(pacman)) install.packages("pacman")
pacman::p_load(
  cem, cobalt, fixest, gtExtras, here,
  labelled, RColorBrewer, rlist, scales, tidyverse, estimatr, modelsummary,
  fastDummies
)
pacman::p_load_gh("rstudio/gt")

# Read and clean data

df_basic <- 
  read_csv(here::here("/masters_thesis/data/panel/dat_basic.csv")) |> 
  filter(wage_per_hour > 700, wage_per_hour < 10000)

df_cov <-
  read_csv(here::here("/masters_thesis/data/panel/dat_panel_cov.csv")) |> 
  mutate(d_regular_same_strong= if_else(regular_same <= 1, 1, 0),
         d_regular_same_weak = if_else(regular_same <= 2, 1, 0))

# Prepare data for analysis
## Filtering regular and haken
df_full <- df_basic |> 
  left_join(df_cov, by = c("ID", "year"))|> 
  filter(firm_size <= 12) |> 
  mutate(post_treat = if_else(year >= 2020, 1, 0),
         age_10s = age %/% 10,
         d_position = if_else(position <= 7, 1, 0),
         small_firm = if_else(firm_size <= 7, 1, 0),
         d_term_fixed = if_else(d_term_fixed == 1, 1, 0),
         d_contract_change = if_else(d_reg_nonreg == 1 | q_nonreg_reg == 1,
                                     1, 0))

# 2017年の時点で契約雇用期間のあるIDを特定
id_fixed_term_2017 <- df_full |> 
  filter(year == 2017, d_term_fixed == 1) |> 
  pull(ID)
df_full <- df_full |>
  filter(ID %in% id_fixed_term_2017)

# IDレベル処置群
id_treated <- df_full |> 
  group_by(ID) %>%
  filter(
    year_entry_current >= 2013 & year_entry_current <= 2017
  ) |> 
  pull(ID)
df_treated <- 
  df_full |> 
  filter(ID %in% id_treated) |> 
  mutate(treat = 1,
         post_treat = case_when(
           year_entry_current == 2013 & year >= 2018 ~ 1,
           year_entry_current == 2014 & year >= 2019 ~ 1,
           year_entry_current == 2015 & year >= 2020 ~ 1,
           year_entry_current == 2016 & year >= 2021 ~ 1,
           year_entry_current == 2017 & year >= 2022 ~ 1,
           TRUE ~ 0),
         relativetime = year - year_entry_current - 5)

# IDレベル対照群
id_never <- df_full |> 
  group_by(ID) %>%
  filter(
    year_entry_current <= 2012 | year_entry_current >= 2018
  ) |> 
  pull(ID)
df_never <- 
  df_full |> 
  filter(ID %in% id_never) |> 
  mutate(treat = 0,
         relativetime = year - year_entry_current - 5,
         post_treat = NA)

# 介入群・対照群のデータをマージする
df_full <- 
  rbind(df_treated, df_never)

df_full <- 
df_full |> 
  group_by(ID) |> 
  mutate(first.treat = first(year[post_treat == 1], na_rm = T)) |> 
  mutate(first.treat = replace_na(first.treat, 0),
         d_term_fixed = 1- d_term_fixed) |> 
  ungroup()


```


## Distribution
```{r cohort construct, echo=FALSE}
table(df_full$year_entry_current)

table(df_full$month_entry_current)

table(df_full$)

hist <- ggplot(df_full, aes(x = year_entry_current))+
  geom_histogram() +
  scale_x_continuous(breaks = seq(1955,2022,1))

hist

hist2 <- ggplot(df_full, aes(x = month_entry_current))+
  geom_histogram() +
  scale_x_continuous(breaks = seq(1,12,1))

hist2

hist3 <- ggplot(df_full, aes(x = ))+
  geom_histogram() +
  scale_x_continuous(breaks = seq(1,12,1))

hist3
```

## Transition of the Outcome (2013 cohort)
```{r transition, echo=FALSE}

# 2013年に現職に就いたコホートをそれ以降に現職についたコホートと比較
df_2013_cohort <- 
  df_full |> 
  filter(year_entry_current > 2012) |> 
  mutate(treated = if_else(year_entry_current == 2013, 1, 0))

table(df_2013_cohort$treated)

# 雇用契約期間のある人の割合を計算
df_ft <- 
  df_2013_cohort |> 
  group_by(treated, year) |> 
  summarise(mean_ft = mean(d_term_fixed))
    
t <-
  ggplot(df_ft, 
         aes(x = year, y = mean_ft, 
             color = as.factor(treated))) +
  geom_line() + 
  geom_point() +
  labs(x = "Year",
       y = "Proportion of Fixed Term Contract",
       color = "treated") + 
  theme_minimal()  

t

df_wage <- 
  df_2013_cohort |> 
  group_by(treated, year) |> 
  summarise(mean_wage = mean(logwage))
    
t2 <-
  ggplot(df_wage, 
         aes(x = year, y = mean_wage, 
             color = as.factor(treated))) +
  geom_line() + 
  geom_point() +
  labs(x = "Year",
       y = "Proportion of Fixed Term Contract",
       color = "treated") + 
  theme_minimal()  

t2

```

## Event Study Analysis (2013 cohort) {.tabset }

### Estimated Model

- Consider the situation that the timing of policy intervention across individuals are equal.
- $y_{i,t}$ is the outcome variable of worker $i$, in year $t$. $T^*$ is the year of treatment and $\beta_{T^* -1}$ is normalised to zero. 

$$
\begin{equation*}
y_{i,t} = \alpha_i + \delta_t + \sum_{r \neq T^* -1} \mathbb{1}(t = r) Treated_i \times \beta_r + \epsilon_{i, t}
\end{equation*}
$$

### NO controll variables{.tabset}

#### d_term_fixed
```{r event study, echo=FALSE}

reg1 <- 
  feols(d_term_fixed ~ i(year, treated, ref=2017) | ID + year,
        data = df_2013_cohort)

iplot(reg1)

```


#### wage
```{r event study2, echo=FALSE}

reg2 <- 
  feols(logwage ~ i(year, treated, ref=2017) | ID + year,
        data = df_2013_cohort)

iplot(reg2)

```

### Controlling age and college education{.tabset}

#### d_term_fixed
```{r event study3, echo=FALSE}

reg3 <- 
  feols(d_term_fixed ~ i(year, treated, ref=2017) + edu_cg + age| ID + year,
        data = df_2013_cohort)

iplot(reg3)

```

#### wage
```{r event study4, echo=FALSE}

reg4 <- 
  feols(logwage ~ i(year, treated, ref=2017)+ edu_cg + age | ID + year,
        data = df_2013_cohort)

iplot(reg4)

```
